Full-core analysis of thorium-fueled Molten Salt Breeder Reactor using the SERPENT 2 Monte Carlo code

### 2017-08-31 discussion.tex
update ans paper to recent publications

\section{Discussion}
This work demonstrated that, given infinite
reprocessing and \gls{MOX} fabrication capacities,
France, by receiving \gls{UNF} from other \gls{EU} nations,
can transition into a full \gls{SFR} fleet
with installed capacity of 60,000 MWe by 2076.
The initial fuel demand is filled by \gls{MOX} from
reprocessed \gls{UNF}, which later on
will be met by \gls{MOX} created from recycled \gls{MOX}.

Since most \gls{EU} nations do not have an operating \gls{UNF}
repository or a management plan, they have a strong incentive
to send all their \gls{UNF} to France. Especially, the nations
with aggressive nuclear reduction can phase out nuclear
without constructing a High Level Waste repository. France has a financial
incentive to take this fuel, since reuse of used fuel from
other nations will allow France to meet their MOX demand
without new construction of \glspl{LWR}.

Though complex political and economic factors have not been
addressed, and various assumptions were made for this scenario,
this option may hold value for the \gls{EU} as a nuclear community,
and for France to advance into a closed fuel cycle.

>>>>

\section{Discussion}
This work demonstrated that, with reprocessing capacity of 250 MTHM per month,
and a fabrication capacity of 300 MTHM per month,
France, by receiving \gls{UNF} from other \gls{EU} nations,
can transition into, for unchanging nuclear electricity demand,
a fully \gls{SFR} fleet
with installed capacity of 66,000 MWe by 2076.
\gls{MOX} from reprocessed \gls{UNF} meets the initial fuel demand,
which later on is supplied by \gls{MOX} created from recycled \gls{MOX}.

Since most \gls{EU} nations do not have an operating \gls{UNF}
repository or a management plan, they have a strong incentive
to send all their \gls{UNF} to France. The nations
with aggressive nuclear reduction will be able phase out nuclear
without constructing a High Level Waste repository. France has an
incentive to take this fuel, since reuse of used fuel from
other nations will allow France to meet their MOX demand
without new construction of \glspl{LWR}.

Though complex political and economic factors are not
addressed, and various assumptions present for this scenario,
this option may hold value for the \gls{EU} as a nuclear community,
and for France to advance into a closed fuel cycle.

### 2017-08-31 introduction.tex
update ans paper to recent publications

\section{Abstract}
The French strategy recommended by 2012-2015 Commission Nationale d'Evaluation reports
\cite{noauthor_cne2_nodate} emphasizes preparation for a transition from \glspl{LWR} to \glspl{SFR}.
This paper uses \Cyclus to explore the feasibility of using \gls{UNF} from other EU nations
for French transition into a \gls{SFR} fleet without additional construction of \glspl{LWR}.
A \Cyclus simulation is run from 1950 to 2160 for EU to track the \gls{UNF} mass
and to determine the necessary reprocessing and \gls{MOX} fabrication capacity to support
the transition into \glspl{SFR}. The study concludes that France can avoid deployment
of additional \glspl{LWR} by accepting \gls{UNF} from other EU nations.

\section{Introduction}
This paper uses \Cyclus, the agent-based simulator \cite{huff_fundamental_2016} to analyze
the future nuclear inventory in the European Union. This paper focuses on the used fuel
inventory in \gls{EU} member states in 2050, and analyzes a potential strategy of used fuel
management.
A major focus of this paper is to determine the extent to which France has an incentive
to receive all the \gls{UNF} from \gls{EU} nations to create \gls{MOX}.
The \gls{MOX} created will fuel French transition to a \gls{SFR} fleet
and may allow France to avoid building additional \glspl{LWR}.

Past research, which focuses solely on France, has made the assumptions that additional \glspl{LWR},
namely \glspl{EPR} are constructed in order to supply \gls{UNF} required
for \gls{MOX} production \cite{carre_overview_2009, martin_symbiotic_2017, freynet_multiobjective_2016}.
There has been studies on implementation of partitioning and transmutation
in a regional (European) context, with \glspl{ADS} and Gen-IV reactors \cite{fazio_study_2013}.
There has been little attention in reprocessing legacy \gls{UNF} from other
EU nations to produce \gls{MOX} for the newly deployed \glspl{SFR}.
The present work finds that this collaborative strategy can reduce the
need to construct additional \glspl{LWR} in France.

\section{Methodology}
The work relies on \Cyclus, an agent-based simulator, to simulate the nuclear fuel cycle
and track material flows in \gls{EU} nations. The \gls{PRIS} open-source 
database from \gls{IAEA} was used to populate the simulation with deployment 
information. That database is imported as a csv file, listing the country, reactor unit, type, net capacity (MWe), status,
operator, construction date, first criticality date, first grid date, commercial date, shutdown
date (if applicable), and unit capacity factor for 2013. Then only the \gls{EU} countries are extracted
from the csv file. A python script is written up to generate a \Cyclus input file from the csv file,
which lists the individual reactor units as agents. After running the \Cyclus input file,
the output file is analyzed by another python script. All the scrips and data used
in this paper are available in \url{https://github.com/jbae11/transition-scenarios}.

Two \Cyclus simulations are run for this paper. 
The first simulation calculates
how much used fuel and tailings \gls{EU} nations accumulate from 1970 to 2050,
as well as the amount of \gls{MOX} that can be created with the \gls{UNF} inventory.
The paper models a once-through cycle for all 
\gls{EU} nations with the exception of France. France can reprocess used \gls{UOX} and \gls{MOX} to
produce \gls{MOX} from reprocessed plutonium and depleted uranium (tailings).
The simulation assumes \gls{MOX} is reprocessed infinitely.

After obtaining the \gls{UNF} inventory of all \gls{EU} in 2050, the second
simulation is run where the \gls{UNF} inventory is reprocessed and
used as fuel for the newly deployed \gls{SFR} reactors.
The \glspl{SFR} are deployed to make up for the decommissioned capacity
of \glspl{LWR} in France, to remain a constant installed capacity of $60,000$ MWe up to 2160.
\gls{SFR} reactors in this paper models after the ASTRID reactor,
and use \gls{MOX} fuel created from 11\% reprocessed plutonium
and 89\% tailings to a burnup
of approximately 100 GWdth/t. The high burnup allows breeding of plutonium.
Eventually, the entire fleet
of \glspl{SFR} are fueled by \gls{MOX} created from recycled \gls{MOX}.

\subsection{Assumptions}
This paper makes the following assumptions:
\begin{itemize}
	\item \gls{SFR} technology available for deployment in 2040
	\item Decay has no effect on reprocessing viability
	\item Reactor construction is always completed on time 
	\item Separated uranium is stockpiled
	\item \glspl{LWR} have a lifetime of 60 years, unless stated otherwise (early shutdown)
	\item Newly deployed \glspl{SFR} have a lifetime of 80 years.
	\item (Only for SFR Case) Reprocessing and \gls{MOX} fabrication begins in 2020.
	\item (Only for SFR Case) French nuclear capacity remains constant at 60,000 MWe
	\item (Only for SFR Case) Infinite reprocessing and fabrication capacity
\end{itemize}

\subsection{Deployment Timeline}
Projections of future reactor deployment in this simulation were
assessed based on analysis from references such as \gls{PRIS} for reactors planned for construction \cite{iaea_pris_nodate},
the World Nuclear Association and two other papers for future plans in EU nations
\cite{world_nuclear_association_nuclear_2017, joskow_future_2012, hatch_politics_2015}.
The projections extend to 2050 at the latest. This allows the simulation to take place from
1970 to 2050, the latest foreseeable future. The specific plans for each \gls{EU} nation are explained
in detail in later sections.

It is also assumed that all reactors that are 
currently operating have a lifetime of 60 years, unless their government plans
early shutdown. This will approximate when and how many \glspl{SFR} need to be built
to make up for the shutdown of \glspl{LWR}.

@@

From 2040, when \gls{SFR}s become available,
600-MWe \gls{SFR}s are deployed to make up for the 
decommissioned \gls{LWR} capacities. Note that a second
separate simulation is run to emphasize France apart from
all other EU nations.

Initially in 2040, 22 \gls{SFR}s
are deployed for the previously decommissioned
\gls{LWR}s. From then, \glspl{SFR} are deployed to
make up for the decommissioned \gls{LWR} capacity.
This results in an installed capacity of 60,000 MWe
of \gls{SFR} by 2076.

\begin{figure}[htbp!]
	\begin{center}
		\includegraphics[width=\columnwidth]{./images/french-transition/number_plot.png}
	\end{center}
	\caption{French Transition into an SFR Fleet}
	\label{fig:sfr_num}
\end{figure}
\FloatBarrier

\Cref{fig:sfr_num} displays
the French transition into \glspl{SFR} over time.
The steep transition from 2035 to 2060 is due mainly to
French aggressive growth from 1975 to 2000. Note the jump in
2040 is due to an attempt to make up for the gap between the
mass decommission of old \glspl{LWR} and the availability
of \glspl{SFR}.

\subsection{Depletion Calculations}
Depletion calculations of the nuclear fuel are recipe-based, such that a fresh 
and used fuel recipe is used for each reactor type.
For the compositions of the fuel, a reference depletion calculation
from ORIGEN is used (see \cref{tab:comp}). The recipe has also been used for
\cite{wilson_adoption_2009}.

\subsection{Scenario Descriptions}
The simulation follows the model fuel cycle, where a `source'
provides natural uranium, which is enriched by an 'enrichment'
facility to produce \gls{UOX}, while disposing enrichment waste (tailings)
to the 'sink' facility. The enriched \gls{UOX} is used
in the \gls{LWR}s and \gls{UOX} waste is produced. The used fuel
is then reprocessed to separate plutonium and uranium.
The plutonium is mixed with depleted uranium (tailings) to \gls{MOX}.
The reprocessed uranium is stockpiled. The cycle is illustrated in
\cref{diag:fc}.

The second scenario separates plutonium from the \gls{UNF}
inventory from the previous simulation. The separated
plutonium is mixed with the depleted uranium inventory from the previous simulation
to create \gls{MOX}, which is used in the \gls{SFR}s. The used
\gls{MOX} is also reprocessed to extract plutonium, which is also
mixed with depleted uranium to produce \gls{MOX}.

>>>>

\section{Abstract}
The French 2012-2015 Commission Nationale d'Evaluation reports
\cite{noauthor_cne2_nodate} emphasize preparation for a transition from \glspl{LWR} to \glspl{SFR}.
This paper uses \Cyclus to explore the feasibility of using \gls{UNF} from other EU nations
for French transition into a \gls{SFR} fleet without additional construction of \glspl{LWR}.
A \Cyclus simulation ran from 1950 to 2160 for EU to track the \gls{UNF} mass
and tails inventory to support
the transition into \glspl{SFR} (66GWe - 110 \glspl{SFR}). The study concludes that France can avoid deployment
of additional \glspl{LWR} by accepting \gls{UNF} from other EU nations.

\section{Introduction}
We used \Cyclus to analyze
the future nuclear inventory in the European Union. \Cyclus is an agent-based extensible
framework for modeling the flow of material through future nuclear cycles \cite{huff_fundamental_2016}.
This paper focuses on the used fuel
inventory in \gls{EU} member states in 2050, and focuses on a potential strategy of used fuel
management.
A major focus of this paper is to determine the extent to which France has an incentive
to receive all the \gls{UNF} from \gls{EU} nations to create \gls{MOX}.
The \gls{MOX} created will fuel French transition to a \gls{SFR} fleet
and allows France to avoid building additional \glspl{LWR}.

Past research focused solely on France typically assumes that additional \glspl{LWR},
namely \glspl{EPR} supply \gls{UNF} to produce \gls{MOX} \cite{carre_overview_2009, martin_symbiotic_2017, freynet_multiobjective_2016}.
Studies exist on implementation of partitioning and transmutation
in a regional (European) context, with \glspl{ADS} and Gen-IV reactors \cite{fazio_study_2013}.
There is little attention paid to reprocessing legacy \gls{UNF} from other
EU nations to produce \gls{MOX} for the newly deployed \glspl{SFR}.
The present work finds that this collaborative strategy can reduce the
need to construct additional \glspl{LWR} in France.

\section{Methodology}

The nuclear history of EU nations are modeled, using the \gls{PRIS} open-source 
database from \gls{IAEA}. That database is imported as a csv file, to populate the simulation
with deployment information, listing the country, reactor unit, type, net capacity (MWe), status,
operator, construction date, first criticality date, first grid date, commercial date, shutdown
date (if applicable), and unit capacity factor for 2013. Then only the \gls{EU} countries are extracted
from the csv file. A python script is written up to generate a \Cyclus input file from the csv file,
which lists the individual reactor units as agents. After running the \Cyclus input file,
another python script analyzes the output file. All the scripts and data used
in this paper are available in \cite{jin_whan_bae_2017_854820}.
%% Probably a separate repository is needed..?

Two \Cyclus simulations are run for this paper. 
The first simulation calculates
the mass and composition of used fuel and tails \gls{EU} nations accumulate from 1970 to 2050,
as well as the amount of \gls{MOX} that the \gls{UNF} inventory creates.
All EU nations with the exception of France adopts a once-through fuel cycle.
France can reprocess used \gls{UOX} and \gls{MOX} to
produce \gls{MOX} from reprocessed plutonium and depleted uranium (tails).
The simulation assumes infinite \gls{MOX} reprocessing.

%%% PASSIVE PHRASE WHAT TO DO
After obtaining the \gls{UNF} inventory of all \gls{EU} in 2050, the second
simulation runs where the \gls{UNF} inventory is reprocessed and used
as fuel for the newly deployed \gls{SFR} reactors.
\gls{SFR} reactors in this paper model after the ASTRID reactor.
ASTRID-type \glspl{SFR} make up for the decommissioned capacity
of \glspl{LWR} in France, to remain a constant installed capacity of $66,000$ MWe up to 2160.
It is assumed that ASTRID-type reactors use \gls{MOX} fuel created from 11\% reprocessed plutonium
and 89\% tails and burns the \gls{MOX} fuel to approximately 100 GWdth/t.
The high burnup allows breeding of plutonium.
Eventually, the  \gls{MOX} created from recycled \gls{MOX}
fuels the entire fleet of 110 \glspl{SFR}.

\subsection{Assumptions}
The simulation ran for this paper had the following assumptions:
\begin{itemize}
	\item \gls{SFR} technology is available for deployment in 2040.
	\item Decay is not taken into account.
	\item Reactor construction is always completed on time.
	\item Separated uranium is unused and stockpiled.
	\item \glspl{LWR} have an assumed lifetime of 60 years, unless shut down prematurely.
	\item Newly deployed \glspl{SFR} have a lifetime of 80 years.
	\item Additional assumptions in the \gls{SFR} case include:
	\begin{itemize}
		\item Reprocessing and \gls{MOX} fabrication begins in 2020.
		\item French nuclear capacity remains constant at 66,000 MWe.
		\item Reprocessing and fabrication capacity is unlimited.
	\end{itemize}
\end{itemize}

\subsection{Deployment Timeline}
Projections of future reactor deployment in this simulation is based on assessment of analyses
from references such as \gls{PRIS} for reactors planned for construction \cite{iaea_pris_nodate},
the World Nuclear Association and two other papers for future plans in EU nations
\cite{world_nuclear_association_nuclear_2017, joskow_future_2012, hatch_politics_2015}.
The projections extend to 2050 at the latest. This allows the simulation to take place from
1970 to 2050, the latest foreseeable future. Later sections explain, in detail, the specific plans for each \gls{EU} nation.

Figure \ref{fig:eu_pow} displays the
timeseries of installed capacity in \gls{EU} nations.

\begin{figure}[htbp!]
	\begin{center}
		\includegraphics[width=\columnwidth]{./images/eu_future/power_plot.png}
	\end{center}
	\caption{Timeseries of installed nuclear capacity in \gls{EU}.}
	\label{fig:eu_pow}
\end{figure}
\FloatBarrier

@@

Once \glspl{SFR} become available, in 2040,
600-MWe \glspl{SFR} are deployed to make up for the 
decommissioned \gls{LWR} capacities. 
This results in an installed capacity of 66,000 MWe
of \gls{SFR} by 2076, when the last \gls{LWR} decommissions.

\begin{figure}[htbp!]
	\begin{center}
		\includegraphics[width=\columnwidth]{./images/french-transition/power_plot.png}
	\end{center}
	\caption{French Transition into an SFR Fleet}
	\label{fig:sfr_num}
\end{figure}
\begin{figure}[htbp!]
	\begin{center}
		\includegraphics[width=\columnwidth]{./images/french-transition/sfr_deploy.png}
	\end{center}
	\caption{Deployment of French \glspl{SFR} and total installed capacity}
	\label{fig:dep}
\end{figure}
\FloatBarrier

\Cref{fig:sfr_num} and \cref{fig:dep} display
the French transition to \glspl{SFR} over time.
The steep transition from 2040 to 2060 reflects the scheduled
decommissioning of reactors built in the 1975-2000
era of aggressive nuclear growth in France.

\subsection{Material Definitions}
Depletion calculations of the nuclear fuel are recipe-based, such that a fresh 
and used fuel recipe is used for each reactor type.
For the compositions of the fuel, a reference depletion calculation
from ORIGEN is used. The recipe has also been used for
\cite{wilson_adoption_2009}.

\subsection{Scenario Descriptions}
The simulation follows the model fuel cycle
where a `source' provides natural uranium, which is enriched by an 'enrichment'
facility to produce \gls{UOX}, while disposing enrichment waste (tails)
to the 'sink' facility. The enriched \gls{UOX} fuels
the \gls{LWR}s and \gls{UOX} waste is produced. The used fuel
is sent to a pool to cool for 3 years \cite{carre_overview_2009}.
The cooled fuel is then reprocessed to separate plutonium and uranium,
or sent to a repository.
The plutonium mixed with depleted uranium (tails) makes \gls{MOX}.
The reprocessed uranium is unused and stockpiled. Uranium is reprocessed
in order to separate the raffinate (Minor actinides and fission products)
from 'usable' material. Though not utilized in this paper, reprocessed
uranium may substitute depleted uranium for \gls{MOX} production. In this
paper, there was sufficient depleted uranium inventory that using reprocessed
uranium was not considered. However, further in the future where the depleted
uranium inventory drains, reprocessed uranium (or, natural uranium) will need to be utilized.

### 2017-08-31 results.tex
update ans paper to recent publications

\begin{table}[h]
	\centering
	\scalebox{0.7}{
		\begin{tabular}{|c|c|c|c|}
			\hline
			Category & Unit & Value & Specifics\\ \hline
			Total UOX Usage & MTHM & 178,865 &  \\ \hline
			Total MOX Usage & MTHM & 8,909 & \\ \hline
			Total Used UOX Stored & MTHM & 157,472 & \gls{UNF} that are not reprocessed\\ \hline
			Total Used  MOX Stored & MTHM & 679 & \gls{UNF} that are not reprocessed \\ \hline
			Total Tailings & MTHM & 1,063,909 & \\ \hline
			Total Natural U Used & MTHM & 1,251,658 & \\ \hline
		\end{tabular}}
		\caption{Simulation Results for Historical Nuclear Operation of \gls{EU} Nations}
		\label{tab:sim_result}
		\end {table}

		\Cref{tab:sim_result} lists the important metrics
		obtained from the first simulation. The following
		values are the \gls{EU} inventory and history at year 2050.

		Figures \ref{fig:eu_num} and \ref{fig:eu_pow} display the
		timeseries of number of reactors and installed capacity in \gls{EU} nations.

		\begin{figure}[htbp!]
			\begin{center}
				\includegraphics[width=\columnwidth]{./images/eu_future/number_plot.png}
			\end{center}
			\caption{Timeseries of number of reactors in \gls{EU}.}
			\label{fig:eu_num}
		\end{figure}

		\begin{figure}[htbp!]
			\begin{center}
				\includegraphics[width=\columnwidth]{./images/eu_future/power_plot.png}
			\end{center}
			\caption{Timeseries of installed nuclear capacity in \gls{EU}.}
			\label{fig:eu_pow}
		\end{figure}
		\FloatBarrier

		Figures \ref{fig:eu_tail} and \ref{fig:eu_snf} show the 
		timeseries of mass of tailings and used fuel accumulation in \gls{EU}.

		Figure \ref{fig:eu_fuel} shows the amount of fuel used in \gls{EU}.

		\begin{figure}[htbp!]
			\begin{center}
				\includegraphics[width=\columnwidth]{./images/eu_future/tailings.png}
			\end{center}
			\caption{Timeseries of Tailings Mass in the \gls{EU}.}
			\label{fig:eu_tail}
		\end{figure}

@@

		\begin{figure}[htbp!]
			\begin{center}
				\includegraphics[width=\columnwidth]{./images/eu_future/snf.png}
			\end{center}
			\caption{Timeseries of Used Nuclear Fuel in \gls{EU}.}
			\label{fig:eu_snf}
		\end{figure}
		\FloatBarrier

		\begin{table}[h]
			\centering
			\begin{tabular}{|c|c|c|}
				\hline
				Isotope & Mass Fraction in Used Fuel [\%] & Quantity [t] \\ \hline
				Total & .9358 & 1,473 \\ \hline
				Pu238 & .0111 & 17.47 \\ \hline
				Pu239 & .518 & 815.7 \\ \hline
				Pu240 & .232 & 365.33 \\ \hline
				Pu241 & .126 & 198.41 \\ \hline
				Pu242 & .0487 & 76.68 \\ \hline
			\end{tabular}
			\caption{Plutonium From Used Fuel}
			\label{tab:pu}
		\end{table}

		To create \gls{MOX} for an ASTRID, 11\% Pu and 89\% depleted uranium is used.
		Thus $1,473$ tons of plutonium yields $13,390$ tons of
		\gls{MOX}. \Cref{tab:pu} lists the isotope, mass fraction,
		and quantity of plutonium that can be obtained from the 2050 \gls{UNF} inventory.

@@

		From Varaine et al. \cite{marsaultmarie-sophie_pre-conceptual_2012}, a French
		ASTRID-type \gls{SFR} of capacity 600 MWe needs $1.225$ tons of
		plutonium a year, with an initial plutonium loading of $4.9$ tons. 
		Thus, the number of \glspl{SFR} that can be loaded with the reprocessed
		plutonium from \gls{UNF} can be estimated to $\frac{1,473}{4.9} \approx 300$ \glspl{SFR},
		assuming infinite reprocessing and fabrication capacity as well as
		abundant depleted uranium supply.

		Also, assuming that \gls{MOX} can be recycled indefinitely,
		used \gls{MOX} from an ASTRID reactor
		contains enough plutonium to produce a \gls{MOX} fuel with
		the same mass, if mixed with depleted uranium. For example,
		used \gls{MOX} from an ASTRID reactor is assumed to be 12.6\% plutonium
		in this simulation (see \cref{tab:comp}), whereas a fresh \gls{MOX} is 11\% plutonium.
		Separating plutonium from used \gls{MOX} from
		an ASTRID reactor can create \gls{MOX} of the mass of used \gls{MOX}.
		The plutonium breeding ratio in this simulation is thus assumed to be
		$\approx 1.145$.

		The second scenario, with the tailings and used \gls{UOX}
		inventory, evaluates if the French can transition into \gls{SFR}
		without constructing additional \gls{LWR}s. This simulation
		assumed infinite reprocessing and fabrication capacity.

		\Cref{fig:fuel} shows the timeseries mass of \gls{MOX} used in the 
		\gls{SFR}s separated by their origin.
		Note that the plot shows \gls{MOX}
		accumulation prior to \gls{SFR} deployment from 2020.

		\begin{figure}[htbp!]
			\begin{center}
				\includegraphics[width=\columnwidth]{./images/french-transition/where_fuel.png}
			\end{center}
			\caption{Timeseries of fuel used in the \gls{SFR}s [tons]}
			\label{fig:fuel}
		\end{figure}

		\Cref{fig:reprocess_waste} shows the amount of reprocessing waste
		(minor actinides, fission products) over time. Note that 
		reprocessing waste from \gls{UOX} reprocessing is substantially
		greater than waste from \gls{MOX} reprocessing due to its lower
		plutonium and uranium content.

		\Cref{fig:pu_isotopics} shows the isotopics of the plutonium that are
		reprocessed from the used fuel inventory.

		\begin{figure}[htbp!]
			\begin{center}
				\includegraphics[width=\columnwidth]{./images/french-transition/rep_pu.png}
			\end{center}
			\caption{Plutonium timeseries separated by isotope}
			\label{fig:pu_isotopics}
		\end{figure}

		\begin{figure}[htbp!]
			\begin{center}
				\includegraphics[width=\columnwidth]{./images/french-transition/reprocess_waste.png}
			\end{center}
			\caption{Reprocessing Waste for French Transition Scenario.}
			\label{fig:reprocess_waste}
		\end{figure}

		\begin{table}[h]
			\centering
			\scalebox{0.7}{
				\begin{tabular}{|c|c|c|}
					\hline
					Category & Unit & Value  \\ \hline
					Total MOX used & MTHM & 116,115  \\ \hline
					Total \glspl{SFR} Deployed & & 200 \\ \hline
					Total Plutonium Reprocessed & MTHM & 14,414 \\ \hline
					Total MOX from UOX Waste & MTHM & 9,729  \\ \hline
					Total MOX from MOX Waste & MTHM  & 150,426  \\ \hline
					Total Tailings used & MTHM & 105,664 \\ \hline
					Total legacy UNF reprocessed & MTHM & 97,298 \\ \hline
					Total Reprocessed Uranium Stockpile & MTHM & 251,100 \\ \hline
					Total Reprocess Waste & MTHM & 14,414 \\ \hline
				\end{tabular}}
				\caption {\gls{SFR} Simulation Results}
				\label{tab:sfr_sim_result}
				\end {table}

>>>>

\Cref{tab:sim_result} lists the important metrics
obtained from the first simulation. The following
values are the \gls{EU} inventory and history at year 2050,
and will be reprocessed in the second simulation.

\begin{table}[h]
	\centering
		\scalebox{0.77}{
	\begin{tabular}{|c|c|c|c|}
		\hline
		Category & Unit & Value & Specifics\\ \hline
		Total UOX Usage & MTHM & 181,471 &  \\ \hline
		Total MOX Usage & MTHM & 6,302 & \\ \hline
		Total Used UOX Stored & MTHM & 141,659 & \gls{UNF} that is not reprocessed\\ \hline
		Total Used  MOX Stored & MTHM & 3,611 & \gls{UNF} that is not reprocessed \\ \hline
		Total Tailings & MTHM & 1,081,826 & \\ \hline
		Total Natural U Used & MTHM & 1,269,897 & \\ \hline
	\end{tabular}
}
	\caption{Simulation Results for Historical Nuclear Operation of \gls{EU} Nations}
	\label{tab:sim_result}
	\end {table}
	\FloatBarrier

	Figures \ref{fig:eu_tail} and \ref{fig:eu_snf} show the 
	timeseries of mass of tailings and used fuel accumulation in \gls{EU}.
	Figure \ref{fig:eu_fuel} shows the amount of fuel used in \gls{EU}.

	\begin{figure}[htbp!]
		\begin{center}
			\includegraphics[width=\columnwidth]{./images/eu_future/tails.png}
		\end{center}
		\caption{Timeseries of Tails Mass in the \gls{EU}.}
		\label{fig:eu_tail}
	\end{figure}

@@

	\begin{figure}[htbp!]
		\begin{center}
			\includegraphics[width=\columnwidth]{./images/eu_future/snf_discharge.png}
		\end{center}
		\caption{Timeseries of Used Nuclear Fuel in \gls{EU}.}
		\label{fig:eu_snf}
	\end{figure}
	\FloatBarrier

@@

	Reprocessing \gls{UNF} collected from all EU nations can start approximately
	270 \glspl{SFR}, which is more than enough for two generations of 66GWe \gls{SFR}
	fleet. With the \gls{SFR} breeding ratio of over one, France can transition into
	a fully \gls{SFR} fleet without extra construction of \glspl{LWR}.

	From Varaine et al. \cite{marsaultmarie-sophie_pre-conceptual_2012}, a French
	ASTRID-type \gls{SFR} of capacity 600 MWe needs $1.225$ tons of
	plutonium a year, with an initial plutonium loading of $4.9$ tons. 
	Thus, the number of \glspl{SFR} that can be loaded with the reprocessed
	plutonium from \gls{UNF} can be estimated to $\frac{Pu \ from \ legacy \ \gls{UNF}}{4.9} \approx 270$ \glspl{SFR},
	assuming infinite reprocessing and fabrication capacity as well as
	abundant depleted uranium supply.

	Also, assuming that \gls{MOX} can be recycled indefinitely,
	used \gls{MOX} from an ASTRID reactor contains enough plutonium to produce a \gls{MOX} fuel with
	the same mass, if mixed with depleted uranium. For example,
	used \gls{MOX} from an ASTRID reactor is assumed to be 12.6\% plutonium
	in this simulation, whereas a fresh \gls{MOX} is 11\% plutonium.
	Separating plutonium from used \gls{MOX} from
	an ASTRID reactor can create \gls{MOX} of the mass of used \gls{MOX}.
	The plutonium breeding ratio in this simulation is thus assumed to be
	$\approx 1.145$.

	\Cref{fig:fuel} shows \gls{MOX} loaded in the \glspl{SFR} per month.
	The spikes are due to initial fuel demand for new deployment of \glspl{SFR}.
	The initial loading of new \glspl{SFR} are done with the \gls{MOX} created
	from legacy \gls{UNF}. Once there are enough amounts of extra plutonium creation
	by deployed \glspl{SFR}, the legacy \gls{UNF} is no longer used.

	\begin{figure}[htbp!]
		\begin{center}
			\includegraphics[width=\columnwidth]{./images/french-transition/where_fuel.png}
		\end{center}
		\caption{Timeseries of fuel loaded into \glspl{SFR}}
		\label{fig:fuel}
	\end{figure}

	\Cref{fig:reprocess_waste} shows the amount of reprocessing waste
	(minor actinides, fission products) over time. The spikes in the 
	waste discharge is due to large influx of spent fuel from
	decommissioned \glspl{SFR}.\Cref{fig:pu_no_cum} shows the separated plutonium discharge
	per month from the reprocessing plant. The plutonium outflux
	does not precisely follow the fuel demand because \Cyclus agents have
	material buffers that store commodity fuel for later usage. 
	\Cref{tab:sfr_sim_result} lists metrics obtained from the second simulation.

	\begin{figure}[htbp!]
		\begin{center}
			\includegraphics[width=\columnwidth]{./images/french-transition/pu.png}
		\end{center}
		\caption{Separated plutonium discharge from Reprocessing Plant}
		\label{fig:pu_no_cum}
	\end{figure}

	\begin{figure}[htbp!]
		\begin{center}
			\includegraphics[width=\columnwidth]{./images/french-transition/reprocess_waste.png}
		\end{center}
		\caption{Reprocessing waste discharge from Reprocessing Plant}
		\label{fig:reprocess_waste}
	\end{figure}

	\begin{table}[h]
		\centering
		\scalebox{0.86}{
			\begin{tabular}{|c|c|c|}
				\hline
				Category & Unit & Value  \\ \hline
				Total MOX used & MTHM & 127,640  \\ \hline
				Total \glspl{SFR} Deployed & & 220 \\ \hline
				Total Plutonium Reprocessed & MTHM & 16,352 \\ \hline
				Total MOX from UOX Waste & MTHM & 6,570  \\ \hline
				Total MOX from MOX Waste & MTHM  & 121,070 \\ \hline
				Total Tails used & MTHM & 116,153 \\ \hline
				Total legacy UNF reprocessed & MTHM & 77,082 \\ \hline
				Total Reprocessed Uranium Stockpile & MTHM & 184,172 \\ \hline
				Total Reprocess Waste & MTHM & 16,352 \\ \hline
			\end{tabular}}
			\caption {\gls{SFR} Simulation Results}
			\label{tab:sfr_sim_result}
			\end {table}
